Demonstrating the Reliability of Randomized Measurement and Verification for Switchable Control Retrofits Using a Large Open-Source Dataset

### 2025-05-14 code/manuscript.Rmd
updated manuscript for discussion

|                        |                                                                  |       |
|------------------|------------------------------------|------------------|
| Parameter              | Description                                                      | Value |
| $\beta_{temp}$         | \% savings from setting $T_{interv}$ 1 °C higher than $T_{base}$ | 0.08  |
| $\beta_{occ}$          | \% savings adjustment during occupied hours                      | 1.2   |
| $\beta_{\text{unocc}}$ | \% savings adjustment during unoccupied hours                    | 0.8   |

@@

>>>>

|                        |                                                                  |       |
|-------------------|------------------------------------|-------------------|
| Parameter              | Description                                                      | Value |
| $\beta_{temp}$         | \% savings from setting $T_{interv}$ 1 °C higher than $T_{base}$ | 0.08  |
| $\beta_{occ}$          | \% savings adjustment during occupied hours                      | 1.2   |
| $\beta_{\text{unocc}}$ | \% savings adjustment during unoccupied hours                    | 0.8   |

@@

## Blocking period impact

Selecting different blocking periods affects how frequently the a M&V
analyst evaluats stopping criteria, thus influencing the duration of the
measurement and verification (M&V) process. Here, we summarize the
advantages and disadvantages of shorter versus longer blocking periods.
As discussed in our previous study, the second step of this randomized
M&V method involves choosing an appropriate blocking period to minimize
potential biases caused by incomplete randomization. For most practical
scenarios, we recommend a blocking period of approximately 12 to 16
weeks, as it typically covers the duration of a season, ensuring a
representative sampling of operational conditions. In general, longer
blocking periods are advantageous when evaluating multiple intervention
strategies or using sampling intervals greater than one day. In such
cases, extended blocking ensures a balanced distribution of both
day-of-week and outdoor weather conditions.

Opting for a shorter blocking period, such as 6 weeks, has the potential
benefit of allowing the stopping criteria to be met more rapidly. We
plotted the percentage of buildings finishing all stopping criteria when
the blocking period is 6 weeks in Figure \@ref(fig:6weekblock). As a
result, when compared to Figure \@ref(fig:intervaltime), the only
difference we found is when sampling at daily interval and not dropping
non-consecutive days, 22% of buildings can get an estimate earlier. This
indicates most buildings require 9 months to meet outdoor weather
conditions starting from January.

```{r 6weekblock, fig.cap = "Time required to satisfy all stopping criteria when using a 6-week blocking period"}

knitr::include_graphics(paste0(fig_path, "6week_time.png"))
```

Sampling at a shorter blocking period also means that the analyst must
perform the hypothesis tests more frequently, which can necessitate
adjusting the significance level using methods such as the Bonferroni
correction to control for increased type-I error risk. On the plus side,
a shorter blocking period can reduce the adverse impact of missing or
problematic data. For example, if an intervention requires fine-tuning
after initial implementation, removing data from the first blocking
period would be less detrimental compared to longer blocking periods,
preserving the overall integrity of the experiment.

## M&V starting time impact

In this study, we consistently set the baseline period to begin on
January 1st, which offers the advantage of capturing colder outdoor
weather conditions early in the M&V process. However, when the baseline
measurements misses the initial winter period, meeting the required
weather condition criteria can potentially take a longer time. To assess
this impact, we repeated the randomized M&V analysis for all buildings
using a new start date in March. As shown in Figure  \@ref(fig:startT),
the new M&V process results in a noticeable delay in satisfying the
stopping criteria. Compared to Figure  \@ref(fig:intervaltime), where a
January start allowed most buildings to finish within 36 weeks, a March
start extended the required duration to 48 weeks for the majority of
buildings. Furthermore, when a longer sampling interval is used or
non-consecutive days are excluded (to avoid carryover effects), some
buildings may require up to 60 weeks to complete the randomized M&V. As
expected, to collect sufficient data representing winter conditions, the
sampling may need to continue until the next January. However, as the
overall data collection period extends, the influence of dropping
non-consecutive days diminishes and becomes less of a concern.

```{r startT, fig.cap = "Time required to satisfy all stopping criteria starting from March"}

knitr::include_graphics(paste0(fig_path, "startT.png"))
```

Similarly, we evaluated the time required to satisfy all stopping
criteria when using a shorter blocking period, as shown in Figure
 \@ref(fig:6weekstartT). Compared to Figure  \@ref(fig:startT), a
significant proportion of buildings completed the randomized M&V by week
42 (mid-December), which is one blocking period earlier than having a
12-week blocking period. This result further highlights that the overall
duration of the randomized M&V process is strongly driven by outdoor
weather. Accordingly, selecting an optimal blocking period should
consider historical or typical meteorological weather file to
effectively minimize the time required.

```{r 6weekstartT, fig.cap = "Time required to satisfy all stopping criteria starting from March and using a shorter blocking period of 6 weeks"}

knitr::include_graphics(paste0(fig_path, "6week_start_time.png"))
```
